%%% Apendix 01
\chapter{List of Publications Generated During PhD Study}

\begingroup
\onehalfspacing
\begin{longtable}{p{0.5in} p{5.0in}}
 2015 & \textbf{Xu, X.} and and J. Wang, Retrieval of aerosol
microphysical properties from AERONET photopolarimetric measurements:
1. Information content analysis, \textit{J. Geophys. Res. Atmos.}, 2015,
120, doi:10.1002/2015JD023108. \\
 2015 & \textbf{Xu, X.},  J. Wang, J. Zeng, R. Spurr, X. Liu, O. Dubovik,
L. Li, Z. Li, M. I. Mishchenko, A. Siniuk, and B. N. Holben, Retrieval of
aerosol microphysical properties from AERONET photopolarimetric
measurements: 2. A new research algorithm and case demonstration,
\textit{J. Geophys. Res. Atmos.}, 2015, 120, doi: 10.1002/2015JD023113.\\
2014 & Wang, J., \textbf{X. Xu}, S. Ding, J. Zeng, R. Spurr, X. Liu, K. Chance, 
and M. Mishchenko, A numerical testbed for remote sensing of aerosols, and its
demonstration for evaluating retrieval synergy from a geostationary satellite
constellation of GEO-CAPE and GOES-R, \textit{Journal of Quantitative
Spectroscopy and Radiative Transfer}, 2014, 146(0), 510-528. \\
2013 & Meland, B. S., \textbf{X. Xu}, D. Henze, and J. Wang, Assessing
remote polarimetric measurement sensitivities to aerosol emissions using
the GEOS-Chem adjoint model, \textit{Atmos. Meas. Tech.}, 2013, 6, 3441-3457.
\\
2013 & \textbf{Xu, X.}, J. Wang, D. K. Henze, W. Qu, and M. Kopacz,
Constraints on aerosol sources using GEOS-Chem adjoint and MODIS
radiances, and evaluation with multisensor (OMI, MISR) data, \textit{J.
Geophys. Res. Atmos.}, 2013, 118(12), 6396-6413. \\
2012 & Wang, J., \textbf{X. Xu}, D. K. Henze, J. Zeng, Q. Ji, S.-C.
Tsay, and J. Huang, Top-down estimate of dust emissions through
integration of MODIS and MISR aerosol retrievals with the GEOS-Chem
adjoint model, \textit{Geophys. Res. Lett.}, 2012, 39(8), L08802. \\
2010 & Wang, J., \textbf{X. Xu}, R. Spurr, Y. Wang, and E. Drury,
Improved algorithm for MODIS satellite retrievals of aerosol optical
thickness over land in dusty atmosphere: Implications for air quality
monitoring in China, \textit{Remote Sensing of Environment}, 2010, 114(11),
2575Ð2583. \\
\end{longtable}
\endgroup

